%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Luis F.}{Santa G.}
\position{Data Scientist{\enskip\cdotp\enskip}Statistician}

\mobile{(+351) 912 960 044}
\email{fernando.santa@novaims.unl.pt}
\linkedin{lfsantag}
\skype{fernando.santa1983}
% \reddit{reddit-id}
% \extrainfo{extra informations}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
\quote{``What we think, we become."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {School of Mathematics and Statistics}
  {University College Dublin (UCD)\\
Belfield, Dublin 4 \\
Dublin\\
Ireland}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for a post-doctoral research fellow}

% How the letter is opened
%\letteropening{Prof. Dr. Frederic Dias}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
    {Luis F. Santa G.~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
I write to show my keen interest in applying to the position as a UCD Post-doctoral Research Fellow Level 1 (reference number: 011556) within UCD School of Mathematics and Statistics. I have recently completed the joint doctorate degree in Information Management from the Universidade Nova de Lisboa (Portugal), University of Münster (Germany), and Universitat Jaume I (Spain), as part of the GEO-C project (\url{www.geo-c.eu}), an H2020 ITN Marie Curie Skłodowska action. I have a MSc in Geomatics and two BScs in Statistics and Cadastral and Geodetic Engineering. I consider that my over ten years of academic and professional background experience conducting statistical data analysis, consultancy, research, and teaching have prepared me well to tackle the challenges described as part of the job profile.\par
UCD highly motivates me due to its academic and research activity. I also find admirable its working environment and the possibility of professional growth that offers to its employees. Moreover, it is exciting that the School of Mathematics and Statistics has been ranked in the top 1\% in the world for both the subjects of Mathematics and Statistics. Additionally, I find very interesting the goals of the VistaMilk SFI Research Centre to integrate agriculture with information and communication technologies (ICT) to bring a sustainable Agri-Tech.\par
My previous experience has been strongly related to define and use statistical modelling for monitoring and predicting processes in several fields as agronomy, climate, ecology, air pollution, public health, transportation, cadastre, geodesy, remote sensing, and urban planning. I have been working with large, noisy, structured, and unstructured datasets for various applications one of which is precision agriculture. For instance, I worked with the Colombian Corporation of Agricultural Research and the Colombian Oil Palm Research Centre developing data analysis to study relationships between soil properties and climate variables with crop yield and the distribution of plagues. I have been working in modelling population dynamics of several species and its relationships with environmental factors. Correctly, I estimated count regression models to explain the weekly number of catches males of Spodoptera Frugiperda, using sexual pheromones, in two different areas as a function of the food supply in the space. Later, I developed an endemic - epidemic approach based on a branching process to predict the number of caught of Anthonomus Grandis in insect traps in cotton growth fields to establish adequate strategies of pest control. I have developed some projects that aimed to analyse the spatial behaviour of multiple processes that occur in the earth such as subsidence, rainfalls distribution, gravimetric and magnetic fields, among others by using Bayesian methods for predicting and defining optimal spatial sampling designs. I studied the distribution of air pollutant (particulate matter 2.5) in Bogota, Colombia, using functional data analysis over the collected data in monitoring stations across the city, the work aimed to understand the spatio-temporal patterns in the distribution of those particles. I have also been studying the spatio-temporal behaviour of various diseases such as dengue, malaria, and gastric cancer, through Bayesian regression modelling to establish several factors associated with the distribution of the number of cases across space and time. During my doctorate, my work was on the study of the urban human dynamics (human activity and human mobility) on datasets coming from social media data, sensors, and telecommunication networks, based on the idea that ICT allow collecting data about city environments and human behaviour through using ubiquitous devices such as mobile phones and sensors.\par
My current work focuses on the use and analysis of data originated by new and massive data sources such as, e.g., sensors that require to rethink software tools, the architecture of systems, and methods of analysis to provide solutions in near real-time. I see contributing to your project with my experience in researching, lecturing, and statistical modelling. In this sense, I think my profile might provide instruments to develop the tasks in a very general framework that could cover from definition and design of systems to strategies of the data analysis.\par
From my point of view, my academic background is a particular combination that allows me to bring distinct and innovative conceptual elements to fill the position of a post-doctoral research fellow. I have profound knowledge in data analysis and, in particular, regression modelling, non-parametric statistics, design of experiments, multivariate methods, machine learning, functional data analysis, multivariate time series, extreme value theory, spatio-temporal statistics, and Bayesian hierarchical models, among others. I have advanced programming skills which can be seen in my management of R, QGIS, SAS, STATA, and SQL, which I acquired self-learning following my interest in always learning new things. All of the above has allowed me to carry out various positions in different roles, in which I have been able to demonstrate my competence. For instance, I have been the main lecturer at the undergraduate and graduate level in two major universities in Colombia for about eight years, teaching from basic to advanced subjects, around six different classes and between 100 and 140 students per semester. This role has required me to develop group management and communication skills, oral and visual communication tools, and the ability to coordinate multiple activities simultaneously, among others. My position as a lecturer has allowed me to work with students in the planning and development of their final bachelor and master projects. Together with my students, we have provided innovative analysis alternatives for many and varied phenomena. Concretely, I have promoted the use of statistics in the analysis and modelling of several fields of knowledge. Many of these works have been published in research journals and presented at conferences and symposiums. I believe that I am a person who has a robust capability to listen, interpret, and guide others. Moreover, I have worked in multidisciplinary teams in research centres and universities, coordinating, suggesting, and implementing data analysis. \par
It is my opinion that becoming part of your team would be highly rewarding. I believe that I can play a proper role in the activities that the position demands. I am willing to work with commitment, enthusiasm, and dedication to achieve the best results. In particular, I consider that I might propose research projects related to the use, analysis, and integration of data coming from several sources, to offer solutions to various problems giving answers to different types of users across several platforms.\par\bigskip
Thank you for considering my application, and I look forward to future communications with you.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
