%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Luis F.}{Santa G.}
\position{Data Scientist{\enskip\cdotp\enskip}Statistician}

\mobile{(+351) 912 960 044}
\email{fernando.santa@novaims.unl.pt}
\linkedin{lfsantag}
\skype{fernando.santa1983}
% \reddit{reddit-id}
% \extrainfo{extra informations}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
\quote{``What we think, we become."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {OUTSYSTEMS}
  {2795-242\\Linda-a-Velha, Portugal}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Data Analyst}

% How the letter is opened
% How the letter is opened
%\letteropening{Dear Dr. Carreras,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
    {Luis F. Santa G.~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}


I am Luis Fernando Santa Guzman, a Colombian statistician and cadastral and geodetic engineer with MSc in Geomatics who finished his doctoral studies at NOVA Information Management School of the Universidade Nova de Lisboa, in the joint doctorate program of Geoinformatics within H2020 Marie Curie Skłodowska action - GEO-C project (\url{www.geo-c.eu}). I consider that my over ten years academic and professional background experience conducting research and teaching, as well as supervising graduation projects has prepared me well to tackle the challenges described as part of the job profile. Furthermore, I would like to express my keen interest in the position as a Data Analyst (Job Id:  887). I got the call through the website LinkedIn.\par 
I am highly motivated with the type of company that is Outsystems. My previous experience has been strongly related to use statistical methods for monitoring and predicting processes in several fields as banking, public health, air pollution, agronomy, among others. I have been performing different roles including data analyst, researching in multidisciplinary teams, lecturer, and adviser. I see contributing to your company with my experience. At this point, I am inclined to believe that I am ready to give a jump to a position with more leadership and that demands from me more than of my skills of strategic development and project management. In this sense, I think my profile might provide instruments to formulate and develop projects in a very general framework that could cover from definition and design of systems to strategies of the data analysis.\par
From my point of view, my academic background is a particular combination that allows me to bring distinct and innovative conceptual elements to face the position of a data scientist analyst. I have profound knowledge in data analysis and, in particular, statistical modelling. I have advanced programming skills which can be seen in my management of R, SQL, and SAS, which I acquired self-learning following my interest in always learn new things. Also, I have been able to demonstrate my competence. For instance, I have been the main lecturer at the undergraduate and graduate level in two major universities in Colombia for about eight years, teaching from basic to advanced subjects, around six different classes and between 100 and 140 students per semester. This role has required me to develop group management and communication skills, oral and visual communication tools, and ability to coordinate multiple activities simultaneously, among others. My position as a lecturer has given me the opportunity to work with students in the planning and development of their final bachelor and master projects. I believe that I am a person who has a robust capability to listen, interpret, and guide others. \par
It is my opinion that becoming part of your analyst team would be highly rewarding. I believe that I can play a proper role in the activities that the position demands. I am willing to work with commitment, enthusiasm, and dedication to achieve the best results. In particular, I consider that I might propose research projects related to the use, analysis, and integration of data coming from several sources, to offer solutions to various problems giving answers to different types of users across several platforms.\par\bigskip

Thank you for considering my application, and I look forward to future communications with you.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
