%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Luis F.}{Santa G.}
\position{Data Scientist{\enskip\cdotp\enskip}Statistician}

\mobile{(+351) 912 960 044}
\email{fernando.santa@novaims.unl.pt}
\linkedin{lfsantag}
\skype{fernando.santa1983}
% \reddit{reddit-id}
% \extrainfo{extra informations}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
\quote{``What we think, we become."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Airbus (Corporate Functions), Airbus (Commercial Aircraft), Airbus Defence and Space}
  {12 Rue Pasteur\\ 92150 Suresnes\\ Francia}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Scientist in Applied Mathematics}

% How the letter is opened
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
    {Luis F. Santa G.~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
I write to show my keen interest in applying to the position of An apprenticeship offer entitled econometrician data scientist in the Airbus. I have recently completed my PhD in Information Management from the Universidade Nova de Lisboa, as part of the Geo-C project (www.geo-c.eu), an H2020 ITN Marie Curie Skłodowska action. I have a MSc in Geomatics and BScs in Statistics and Cadastral and Geodetic Engineering. I consider that my over ten years academic and professional background experience conducting research and teaching, as well as supervising graduation projects in Statistics, Geoinformatics, and Geographic Information Science has prepared me well to tackle the challenges described as part of the job profile.\par

I am highly motivated with the type of company and developed work by Airbus. My previous experience has been strongly related to use spatio-temporal statistics for monitoring and predicting processes in several fields as transportation, public health, ecology, air pollution, agronomy, climate, cadastre, geodesy, remote sensing, and urban planning. My current work focuses on the use and analysis of spatio-temporal data originated by new and massive data sources such as, e.g., social media, sensors, and telecommunication networks that require to rethink software tools, the architecture of systems, and methods of analysis to provide solutions in near real-time. I have been performing different roles including data analyst, researching in multidisciplinary teams, lecturer, and adviser. I see contributing to your department with my experience. At this point, I am inclined to believe that after finishing my PhD I am ready to give a jump to a position with more creative profile and that demands from me more than of my skills of strategic development and project management. In this sense, I think my profile might provide instruments to formulate and develop projects in a very general framework that could cover from definition and design of systems to strategies of the data analysis.\par

From my point of view, my academic background is a particular combination that allows me to bring distinct and innovative conceptual elements to face the position of a scientist in applied mathematics. I have profound knowledge in data analysis and, in particular, of spatio-temporal data, which represent a different paradigm within statistics and data mining. I have advanced programming skills which can be seen in my management of R, QGIS, and SQL, which I acquired self-learning following my interest in always learn new things. All of the above has allowed me to carry out various positions in different roles, in which I have been able to demonstrate my competence. For instance, I have been the main lecturer at the undergraduate and graduate level in two major universities in Colombia for about eight years, teaching from basic to advanced subjects, around six different classes and between 100 and 140 students per semester. This role has required me to develop group management and communication skills, oral and visual communication tools, and ability to coordinate multiple activities simultaneously, among others. My position as a lecturer has given me the opportunity to work with students in the planning and development of their final bachelor and master projects. Together with my students, we have provided innovative analysis alternatives for multiple and varied phenomena that occur on the earth's surface. Correctly, I have promoted the use of spatio-temporal statistics in the analysis and modelling of several field of knowledge. Many of these works have been published in research journals and presented at conferences and symposiums. I believe that I am a person who has a robust capability to listen, interpret, and guide others. Moreover, I have worked in multidisciplinary teams in research centres and universities, coordinating, suggesting, and implementing data analysis. \par
It is my opinion that becoming part of your research team would be highly rewarding. I believe that I can play a proper role in the activities that the position demands. I am willing to work with commitment, enthusiasm, and dedication to achieve the best results. In particular, I consider that I might propose research projects related to the use, analysis, and integration of data coming from several sources, to offer solutions to various problems giving answers to different types of users across several platforms.\par\bigskip

Thank you for considering my application, and I look forward to future communications with you.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
