%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Luis F.}{Santa G.}
\position{Data Scientist{\enskip\cdotp\enskip}Statistician}
\address{R. Santa Bárbara 30 e 32 R/Ch, 1150-289, Lisbon, Portugal}

\mobile{(+351) 912 960 044}
\email{fernando.santa@novaims.unl.pt}
\linkedin{lfsantag}
\skype{fernando.santa1983}
% \reddit{reddit-id}
% \extrainfo{extra informations}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
\quote{``What we think, we become."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {UCL Centre for Advanced Spatial Analysis}
  {The Bartlett Centre for Advanced Spatial Analysis\\ Gower Street\\WC1E 6BT\\London, United Kingdom}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for a research fellow position at the Urban Dynamics Lab (UDL)}

% How the letter is opened
\letteropening{Dear Dr. Elsa Arcaute}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
    {Luis F. Santa G.~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am Luis Fernando Santa Guzman, a Colombian statistician and cadastral and geodetic engineer with MSc in Geomatics who currently finished the doctoral studies at the NOVA Information Management School of the Universidade Nova de Lisboa, in the joint doctorate program of Geoinformatics. I consider that my over ten years academic and professional background experience conducting research and teaching, as well as supervising graduation projects in Statistics, Geoinformatics, and Geographic Information Science has prepared me well to tackle the challenges described as part of the job profile. Furthermore, I would like to express my keen interest in the position as a research fellow in the Urban Dynamics Lab (UDL) at University College London (Ref:1750762). I found the call through the distribution list of H2020 Marie Curie Skłodowska action - GEO-C project (\url{www.geo-c.eu}) of which I was part of as an early stage researcher.

\lettersection{Why The Department of Mathematics and Mathematical statistics?}
I am highly motivated with the type of projects that the department has been developing and leading in the field spatio-temporal data analysis. Specifically, its oriented work to develop new alternatives of statistical analysis. My previous experience has been strongly related to use spatio-temporal statistics for monitoring and predicting processes in several fields as transportation, public health, ecology, air pollution, agronomy, climate, cadastre, geodesy, remote sensing, and urban planning. My current work focuses on the use and analysis of spatio-temporal data originated by new and massive data sources such as, e.g., social media, sensors, and telecommunication networks that require to rethink software tools, the architecture of systems, and methods of analysis to provide solutions in near real-time. I have been performing different roles including data analyst, researching in interdisciplinary teams, lecturer, and adviser. I see contributing to your department with my experience. At this point, I am inclined to believe that I am ready to give a jump to a position with more leadership and that demands from me more than of my skills of strategic development and project management. In this sense, I think my profile might provide instruments to develop the project in a very general framework that could cover from definition and design of systems to strategies of the data analysis.

\lettersection{Why Me?}

From my point of view, my academic background is a particular combination that allows me to bring distinct and innovative conceptual elements to face the position of a postdoc in the Department of Mathematics. I have profound knowledge in data analysis and, in particular, of spatio-temporal data, which represent a different paradigm within statistics and data mining. I have advanced programming skills which can be seen in my management of R, QGIS, and SQL, which I acquired self-learning following my interest in always learn new things. All of the above has allowed me to carry out various positions in different roles, in which I have been able to demonstrate my competence. For instance, I have been the main lecturer at the undergraduate and graduate level in two major universities in Colombia for about eight years, teaching from basic to advanced subjects, around six different classes and between 100 and 140 students per semester. This role has required me to develop group management and communication skills, oral and visual communication tools, and ability to coordinate multiple activities simultaneously, among others. My position as a lecturer has given me the opportunity to work with students in the planning and development of their final bachelor and master projects. Together with my students, we have provided innovative analysis alternatives for multiple and varied phenomena that occur on the earth's surface. Many of these works have been published in research journals and presented at conferences and symposiums. I believe that I am a person who has a robust capability to listen, interpret, and guide others. Moreover, I have worked in interdisciplinary teams in research centres and universities, coordinating, suggesting, and implementing spatio-temporal data analysis. \par
It is my opinion that becoming part of your research team would be highly rewarding. I believe that I can play a proper role in the activities that the position demands. I am willing to work with commitment, enthusiasm, and dedication to achieve the best results. In particular, I consider that I might develop the research project integrating to the analysis other data coming from sources such as city sensors and ubiquitous devices, to offer broader solutions to different types of users across several platforms.\par\bigskip
Thank you for considering my application, and I look forward to future communications with you.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}