Who you are?

The cover letter needs to answer these questions.
Why do your fit? Why do you apply?

We need to say our goals, teaching goals, or research goals... You need to present you as unique, and be persuasive... engagen in your letter

A cover letter is a persuasive document that directly connects you to the department, articulating your future contributions.

You need to do research on the department, 

Dont talk a lot about your research if not in the future contributions...

Adjusting your needs, what they need and how you fit there. Based on what you done, and go 

%%%%%%%

TIPS
- 2 pages max. (1 and half pages)
- 11-12 font size - readible... 
- Personalize: 
- Future-oriented and focused
- Provides evidence...

%%%%%%%%

- Introduction

What position are you applying to?

Open up with a story, more narrative it is an option. Be creative. 

Who are you?


Why are you applying (to this job)?

- Major sections: ( Research / Teaching / Service) it depends of the job position, so read very well the position. 

%%%%%%%%%

- Research section

You need to connect with the department, is not one covering that and I am the person for that. 
Mention to collaboration, how your research can connect with other collaborators in the department.
Emphasize the impact of your research, be proud of your research.
Past publish in this, now we are doing this, and in future we will do that... make connections between past present and future

One paragraph about of my research, other about contributions and last one future.
1. research 
2. so far contribution
3. future contributions

%PRACTICAL

First:
Who I am as researcher and how to connect to the department/

Specifically, I focus on this and this and maybe mention your methods.

I publish in these areas or i have under review in these journals. I have been awarded in this and that. I won this money, from this project...

after, talk about your dissertation and how you contribute:
example, my dissertation is that and the impact is this and that...

Future research one or two paragraphs... I am planning to publish that, and also working to another project... like a short proposal of ideas that you have for a second project.

%%%%%%%%%%%%

- Teaching section

1. Overall pedagogical beliefs and practices, as evidenced in past experiences

They want to know how do you teach and what do you teach... Summary of pedagogical, a summary of the teaching statement.

2. Future experiences: what could you can teach and develop?

You are able to share what you can teach and what they are looking for, if you have a contact in the department ask about information how teaching there... 

How youa can teach a students from different cultures? What kind of courses you can develop? 

3. Who could you supervise?

You should still say which kind of students you can supervise, articulate that.

%PRACTICAL

first paragraph explain research position and how connects
classes that you tough in the past
and future classes 

How your research informs your teaching, in teaching section viceversa.

%%%%%%%%%%%%%%%

3. Service section

Can include:
- Developing policies, curriculum, admissions, etc

- Student association

- Relevant experiences from off-campus

Say something about how connect your research to your community, you are connected with community

%PRACTICAL



%%%%%

Conclusion

- Summarize the value, you bring to the position, department, and institution.

- Connect to department goals, whether they be research-focused, teaching focused or both!

Check the values of the department and rewrite and put in your conlusion maybe.

%%%%%

Storytelling in cover letters:

One question about the research and after another about methods.

easy sentence... 

My sentence

I work on the relationship between social theory and its spatial representation.

The people who is going to read your cl, maybe it is not familiar with your research, maybe they are not experts. 

Have a sentence prepare. Try to concise your research and appealing to your audience. 

%%%

Research beyond the posting... look for everything list of faculties, instutitions realted, research labs,.. try to indicate haw you are going to collaborate about that.  What the department prioritize? Check the funding they have, and mention that you can help to this resources... how many students have in class as average? Maybe they are replacing someone so go for what you can provide more than him, her.

AVOID THE WORD STUDENT!! FELOWSHIP!!!  I am finishing my post-doc...


%%%. Key considerations

Logical ; if the job is teaching focus on teeaching
















