%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {European Joint Doctoral Degree in Geoinformatics} % Degree
    {Universidade Nova de Lisboa, Universitat Jaume I and University of Muenster } % Institution
    {Portugal, Spain and Germany} % Location
    {Sep. 2015 - Nov. 2018} % Date(s)
    { 
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Marie Curie project \href{www.geo-c.eu}{\textit{\textcolor{lightgray}{GEO-C}}} - Enabling Open Cities (Marie-Curie action).}
            \item {Supervisor: Full Prof. Marco Painho}
        \end{cvitems}
     }
    
%\vspace{-4mm}
%---------------------------------------------------------

  \cventry
    {Erasmus Mundus Master in Geospatial Technologies \href{http://mastergeotech.info}{\textit{\textcolor{lightgray}{(GEOTEC)}}}} % Degree
    {Universidade Nova de Lisboa, Universitat Jaume I and University of Muenster} % Institution
    {Portugal, Spain and Germany} % Location
    {Sep. 2013 - Mar. 2015}
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Programming, databases, and data visualization}
            \item {Spatial analysis, geospatial datamining, and data analysis}
        \end{cvitems}
    }

%\vspace{-4mm}
%---------------------------------------------------------

  \cventry
    {Master in Territorial Planning and Environmental Management \href{http://mastergeotech.info}{\textit{\textcolor{lightgray}{(mastergeohis)}}}} % Degree
    {Universitat de Barcelona} % Institution
    {Barcelona, Spain} % Location
    {Sep. 2009 - Jun. 2013}
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Territorial planning and development, regional and local tourism development}
            \item {Planning and management of urban spaces, demographic dynamics and migrations}
        \end{cvitems}
    }

%\vspace{-4mm}
%---------------------------------------------------------

  \cventry
    {Bachelor’s degree in Geoinformation and Geomatics Engineering \href{https://epseb.upc.edu/en/studies/bachelor-s-degree-in-geoinformation-and-geomatics-engineering}{\textit{\textcolor{lightgray}{(UPC)}}}} % Degree
    {Universitat Politècnica de Catalunya} % Institution
    {Barcelona, Spain} % Location
    {Sep. 2004 - Mar. 2008}
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Geographic information and cartography, digital cartography, and GIS databases}
            \item {Mathematical cartography, physical geodesy, and geometric geodesy}
        \end{cvitems}
    }

%\vspace{-4mm}

%---------------------------------------------------------
\end{cventries}
