%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\begin{comment}

hierarchy

Books
“Edited Volumes
Refereed Journal Articles
Book Chapters
Conference Proceedings
Encyclopedia Entries
Book Reviews
Manuscripts in Submission (Give journal title.)
Manuscripts in Preparation
Web-Based Publications
Other Publications (This section can include nonacademic publications, within reason.)”

Excerpt From: Kelsky, Karen. “Professor Is in : The Essential Guide to Turning Your Ph.d. into a Job (9780553419436).” Apple Books. 

\end{comment}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Refereed Journal Articles}

\begin{cventries}

\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Santa, F., Johnson, P.A. {\it (in press)}. Place and people: Spatializing degrees of bonding and bridging social capital {\it Geojournal}}
      \end{cvitems}}


%----------------------------------------------------
\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Johnson, P.A. (2019). Home Range and Habitat: Using platial characteristics to define urban areas from the bottom-up. {\it Transactions in GIS} doi: \url{ https://doi.org/10.1111/tgis.12597}}
      \end{cvitems}}


%----------------------------------------------------
\vspace{-4mm}

  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Oliveira, T., Naranjo-Zolotov, M., Painho, M. (2019). Place and City: toward a geography of engagement. {\it Heliyon}, 5 (8), 1-14. doi: \url{ https://doi.org/10.1016/j.heliyon.2019.e02261}}
      \end{cvitems}}

\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item{{\bf Acedo, A.}, Painho, M., Casteleyn, S., and Roche, S. (2018). Place and City: Toward Urban Intelligence. {\it ISPRS International Journal of Geo-Information}, 7 (9), 346. doi: \url{ https://doi.org/10.3390/ijgi7090346}}
      \end{cvitems}}
      
\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {Portela, M., {\bf Acedo, A.}, Granell-Canut, C. (2018). Looking for “in-between” places. {\it Media Theory}, 2 (1), 108-133. Accessible through \url{https://hal.archives-ouvertes.fr/hal-01870435}}
      \end{cvitems}}

\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Painho, M., and Casteleyn, S. (2017). Place and city: Operationalizing sense of place and social capital in the urban context. {\it Transactions in GIS}, 2017;00:1–16. doi: \url{https://doi.org/10.1111/tgis.12282}}
      \end{cvitems}}      

\vspace{-4mm}
%---------------------------------------------------------
\end{cventries}

\cvsubsection{Conference Proceedings}

\begin{cventries}

\vspace{-4mm}
%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item{{\bf Acedo, A.}, Santa, F., Painho, M., Henriques, R. (2018). Do people develop activities at places in which citizens have a sense of place?. {\it Proceedings AGILE Conference} Accessible through \url{ https://agile-online.org/conference/proceedings/proceedings-2018}}
      \end{cvitems}}

\vspace{-4mm}
%---------------------------------------------------------
   \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item{{\bf Acedo, A.}, Mendoza, G., Painho, M., Casteleyn, S. (2017). One tool to spatiallize all: sense of place, social capital and civic engagement. {\it Proceedings AGILE Conference} Accessible through \url{ https://agile-online.org/conference/proceedings/proceedings-2017}}
      \end{cvitems}}
      
\vspace{-4mm}      

\end{cventries}


\cvsubsection{Manuscripts in Submission}

\begin{cventries}


\vspace{-4mm}

  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {Johnson, P.A., {\bf Acedo, A.}, Robinson, P. (2020 - expected). Canadian Smart Cities: Are we wiring new citizen-local government interactions? {\it The Canadian Geographer/ Le Géographe Canadien (under review)}}
      \end{cvitems}}

\vspace{-4mm}

\end{cventries}

\cvsubsection{Manuscripts in Preparation}

\begin{cventries}

\vspace{-4mm}

%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Naranjo-Zolotov, M. {\it Journal of Environmental Psychology}}
      \end{cvitems}}

\vspace{-4mm}

%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Westerholt, R. {\it International Journal of Geographical Information Science}}
      \end{cvitems}}

\vspace{-4mm}

%---------------------------------------------------------
  \cventry
    {} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {\begin{cvitems} % Description(s)
        \item {{\bf Acedo, A.}, Johnson, P.A. {\it GeoJournal}}
      \end{cvitems}}

\vspace{-4mm}

\end{cventries}
